Figures

### 2019-06-20 figures/07_model-selection.Rmd
hu4 histograms

```{r signif_hu4_lakes}
# compare lakes in signif hu4s
dt        <- readRDS("../data/dt_scaled.rds") %>%
  mutate(signif_hu4 = hu4_zoneid %in% signif_hu4_ids) %>%
  tidyr::gather(key = "key", value = "value", 
                      -lagoslakeid, -hu4_zoneid, -hu12_zoneid, -signif_hu4)

ggplot(data = dt) + 
  geom_histogram(aes(x = value, fill = signif_hu4)) +
  geom_vline(aes(xintercept = median(value, na.rm = TRUE), color = signif_hu4)) +
  facet_wrap(~key)

>>>>

```{r signif_hu4_lakes}
# compare lakes in signif hu4s
dt        <- readRDS("../data/dt_scaled.rds") %>%
  mutate(signif_hu4 = hu4_zoneid %in% signif_hu4_ids) %>%
  tidyr::gather(key = "key", value = "value", 
                      -lagoslakeid, -hu4_zoneid, -hu12_zoneid, -signif_hu4) %>%
  group_by(key, signif_hu4) %>%
  mutate(median = median(value, na.rm = TRUE))

dt_predictors <- dplyr::filter(dt, key %in% 
                                 c("wetland_potential", "tp",
                                   "nitrogen_atmospheric_deposition",
                                   "hu12_baseflow_mean", "clay_pct"))
dt_modelled <- dplyr::filter(dt, key %in% 
                               c("maxdepth", "tn", "soil_org_carbon",
                                 "buffer_cultivated_crops", "corn",
                                 "nitrogen_fertilizer_use"))

ggplot(data = dt_predictors) + 
  geom_histogram(aes(x = value, fill = signif_hu4), alpha = 0.7) +
  geom_vline(aes(xintercept = median, color = signif_hu4), 
             linetype = "dashed") +
  facet_wrap(~key)

ggplot(data = dt_modelled) + 
  geom_histogram(aes(x = value, fill = signif_hu4), alpha = 0.7) +
  geom_vline(aes(xintercept = median, color = signif_hu4), 
             linetype = "dashed") +
  facet_wrap(~key)

fit_tn$formula
